Synpotic Soil Characterization

### 2024-11-11 3-reports/manuscript_figures.Rmd
fix legends and symbols

gg_pca_wle = 
  ggbiplot(pca_overall_wle$pca_int, obs.scale = 1, var.scale = 1, varname.size = 5,
           groups = as.character(pca_overall_wle$grp$transect), 
           ellipse = TRUE, circle = FALSE, var.axes = TRUE, alpha = 1) +
  geom_point(size=3,stroke=1, alpha = 1,
             aes(shape = pca_overall_wle$grp$site,
                 color = groups))+ 
  scale_color_manual(breaks = c("upland", "transition", "wte", "wc"), 
                     values = pal_transect)+
  xlim(-3, 5)+
  ylim(-2.5, 3.5)+
  labs(shape="",
       title = "PCA: WLE")+
  theme_kp()+
  theme(legend.position = "top", legend.box = "vertical")+
  NULL

gg_pca_cb = 
  ggbiplot(pca_overall_cb$pca_int, obs.scale = 1, var.scale = 1, varname.size = 5,
           groups = as.character(pca_overall_cb$grp$transect), 
           ellipse = TRUE, circle = FALSE, var.axes = TRUE, alpha = 0) +
  geom_point(size=3,stroke=1, alpha = 1,
             aes(shape = pca_overall_cb$grp$site,
                 color = groups))+ 
  scale_color_manual(breaks = c("upland", "transition", "wte", "wc"), 
                     values = pal_transect)+
  xlim(-5.5, 3)+
  ylim(-3, 3.5)+
  labs(shape="",
       title = "PCA: CB")+
  theme_kp()+
  theme(legend.position = "top", legend.box = "vertical")+
  NULL

gg_pca_regions = cowplot::plot_grid(gg_pca_wle , gg_pca_cb, nrow = 1)
gg_pca_regions

@@

ggbiplot::ggbiplot(pca_cluster$pca_int, obs.scale = 1, var.scale = 1, varname.size = 5,
                   groups = as.character(pca_cluster$grp$cluster), 
                   ellipse = F, circle = FALSE, var.axes = TRUE, alpha = 0) +
  geom_convexhull(aes(group = pca_cluster$grp$cluster,
                      fill = pca_cluster$grp$cluster), alpha = 0.2)+
  geom_point(size=4,stroke=1, alpha = 1,
             aes(shape = pca_cluster$grp$region,
                 fill = groups))+ 
  scale_shape_manual(values = c(23, 21))+
  scale_color_manual(values = pnw_palette("Sailboat", 3))+
  scale_fill_manual(values = pnw_palette("Sailboat", 3))+
  labs(fill="cluster",
       color = "cluster",
       shape = "region",
       title = "Overall PCA, both regions",
       subtitle = "Surface horizons only")+
  theme_kp()+
  NULL

>>>>

gg_pca_wle = 
  ggbiplot(pca_overall_wle$pca_int, obs.scale = 1, var.scale = 1, varname.size = 5,
           groups = as.character(pca_overall_wle$grp$transect), 
           ellipse = TRUE, circle = FALSE, var.axes = TRUE, alpha = 1) +
  geom_point(size=5,stroke=1, alpha = 1,
             aes(shape = pca_overall_wle$grp$site,
                 fill = groups), 
             stroke = 1)+ 
  scale_color_manual(breaks = c("upland", "transition", "wte", "wc"), 
                     values = pal_transect)+
  scale_fill_manual(breaks = c("upland", "transition", "wte", "wc"), 
                    values = pal_transect)+
  scale_shape_manual(values = c(21, 24, 22))+
  xlim(-3, 5)+
  ylim(-2.5, 3.5)+
  labs(shape="", fill = "", color = "")+ 
  theme_kp()+
  theme(legend.position = "top", legend.box = "vertical")+
  guides(fill = guide_legend(override.aes = list(alpha=1, shape = 21, size = 3)))+
  NULL

gg_pca_cb = 
  ggbiplot(pca_overall_cb$pca_int, obs.scale = 1, var.scale = 1, varname.size = 5,
           groups = as.character(pca_overall_cb$grp$transect), 
           ellipse = TRUE, circle = FALSE, var.axes = TRUE, alpha = 0) +
  geom_point(size=5,stroke=1, alpha = 1,
             aes(shape = pca_overall_cb$grp$site,
                 fill = groups), 
             stroke = 1)+ 
  scale_color_manual(breaks = c("upland", "transition", "wte", "wc"), 
                     values = pal_transect)+
  scale_fill_manual(breaks = c("upland", "transition", "wte", "wc"), 
                    values = pal_transect)+
  scale_shape_manual(values = c(21, 24, 22))+
  xlim(-5, 3)+
  ylim(-2.5, 3.5)+
  labs(shape="", fill = "", color = "")+ 
  theme_kp()+
  theme(legend.position = "top", legend.box = "vertical")+
  guides(fill = guide_legend(override.aes = list(alpha=1, shape = 21, size = 3)))+
  NULL

gg_pca_regions = cowplot::plot_grid(gg_pca_wle , gg_pca_cb, nrow = 1,
                                    labels = c("A: WLE", "B: CB"))
gg_pca_regions

@@

ggbiplot::ggbiplot(pca_cluster$pca_int, obs.scale = 1, var.scale = 1, varname.size = 5,
                   groups = as.character(pca_cluster$grp$cluster), 
                   ellipse = F, circle = FALSE, var.axes = TRUE, alpha = 0) +
  geom_convexhull(aes(group = pca_cluster$grp$cluster,
                      fill = pca_cluster$grp$cluster), alpha = 0.2)+
  geom_point(size=4,stroke=1, alpha = 1,
             aes(shape = pca_cluster$grp$region,
                 fill = groups))+ 
  scale_shape_manual(values = c(23, 21))+
  scale_color_manual(values = pnw_palette("Sailboat", 3))+
  scale_fill_manual(values = pnw_palette("Sailboat", 3))+
  labs(fill="cluster",
       color = "cluster",
       shape = "region")+
  theme_kp()+
  theme(legend.position = c(0.8, 0.75))+
  guides(fill = guide_legend(override.aes = list(shape = 21)))+
  NULL
